### 2019-10-25 paper/conclusion.tex
Matt's comments implemented in Andrei's part

Five different types of initial fissile loadings have been studied for 
transitioning to the thorium fuel cycle in the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR). We 
adopted two different feed mechanisms: thorium feed mechanism and non-thorium 
feed mechanism. Lifetime-long depletion for the whole-core SD-TMSR model was 
performed with reactor-grade Pu, TRU, and $^{233}$U as initial fissile 
materials. Additionally, the dynamics of the effective multiplication factor 
$k_{eff}$, major isotopes mass, neutron energy spectrum, and essential safety 
parameters have been investigated.

>>>>

Five different types of initial fissile loadings are considered to investigate 
transitioning to the thorium fuel cycle in the SD-TMSR. We adopted two 
different feed mechanisms: thorium feed mechanism and non-thorium feed 
mechanism. Lifetime-long depletion for the whole-core SD-TMSR model was 
performed with reactor-grade Pu, TRU, and $^{233}$U as initial fissile 
materials. Additionally, the dynamics of the effective multiplication factor 
$k_{eff}$, major isotopes mass, neutron energy spectrum, and essential safety 
parameters have been investigated.

### 2019-10-25 paper/results.tex
minor changes
Matt's comments implemented in Andrei's part

\subsection{Neutron flux}
Figures~\ref{fig:fast_flux}, \ref{fig:thermal_flux} show the radial 
distribution of fast (energy range between 0.625 eV and 20 MeV) and thermal 
(energy range between 10$^{-5}$ eV and 0.625 eV) neutron flux for three 
different initial fissile materials in the fuel salt ($^{233}$U, reactor-grade 
plutonium, TRU) at startup and at equilibrium (after $\approx 30$ years of 
operation). Actinides evolution and poisonous fission product accumulation 
for various initial fissile compositions demonstrated the different effects on 
the SD-TMSR neutronics performance. For the $^{233}$U case, the thermal neutron 
flux is suppressed at the equilibrium because fissile $^{233}$U in the core is 
being substituted with heavier fissile actinides: $^{235}$U, $^{239}$Pu, and 
$^{241}$Pu. This is in good agreement with results in the literature 
\cite{rykhlevskii2019modeling, ashraf2019whole_core}.
\begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
	\includegraphics[width=\textwidth]{radial_fast_flux_init_vs_eq.png} 
	\caption{Radial fast neutron flux distribution for 3 different initial 
		fuel salt compositions at startup and equilibrium (the fast flux 
		confidence interval $\pm\sigma<2.5$\% for all cases).}
	\label{fig:fast_flux}
\end{figure}

Opposite behavior was observed for the Pu reactor-grade and TRU cases. For 
these cases, the thermal neutron flux is increasing during operation while 
fast neutron flux is decreasing. Fissile plutonium nuclides (generate 
relatively hard spectrum) from initial fuel salt composition is gradually 
substituted with the $^{233}$U (generates relatively soft spectrum), produced 
from the fertile $^{232}$Th. During reactor operation, the $^{233}$U becomes 
primary fissile isotope, which leads to the neutron spectrum softening of the 
reactor. 
\begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
	\includegraphics[width=\textwidth]{radial_thermal_flux_init_vs_eq.png} 
	\caption{Radial thermal neutron flux distribution for 3 different initial 
		fuel salt compositions at startup and equilibrium (the thermal flux 
		confidence interval $\pm\sigma<1.6$\% for all cases).}
	\label{fig:thermal_flux}
\end{figure}

Notably, more changes in thermal neutron flux shape and magnitude for the 
$^{233}$U case were observed in the inner core zone ($R\lesssim150$) than 
in the outer core zone. In contrast, for Pu reactor-grade and TRU cases, 
significant changes were observed for thermal neutron flux in the outer core 
zone and reflector. Additionally, Figure~\ref{fig:thermal_flux} shows 
relatively large changes in thermal flux leakage from the core for the Pu and 
TRU cases. Overall, the SD-TMSR core design was optimized for $^{233}$U 
fissile isotope \cite{li_optimization_2018}; thus, the core geometry (e.g., 
fuel channels lattice pitch) must be re-optimized for another type of fuel to 
obtain better neutronics performance.

\subsection{Temperature coefficient of reactivity}
The temperature coefficient of reactivity quantifies reactivity changes due to 
temperature increase in the core and was calculated in this work as follows:
\begin{align}
\alpha &= \frac{k_{eff}(T_{i+1}) - k_{eff}(T_i)}{k_{eff}(T_{i+1}) 
	k_{eff}(T_{i}) (T_{i+1} - T_i)}
\intertext{where}
k_{eff} &= \mbox{effective multiplication factor} \nonumber \\
T_i &= \mbox{fuel salt temperature in (900 K, 1000 K).} \nonumber
\end{align}

Table~\ref{tab:tcoe} summarizes temperature coefficients calculated for three 
different initial fissile loads at the startup and at the equilibrium. By 
propagating the $k_{eff}$ statistical error provided by SERPENT-2, 
uncertainty for each temperature coefficient was calculated using formula:
\begin{align}
\delta\alpha &= \abs{\frac{1}{T_{i+1} - T_i}} \sqrt{\frac{\delta 
		k_{eff}^2(T_{i+1})}{k_{eff}^4(T_{i+1})}  
	+ \frac{\delta k_{eff}^2(T_i)}{k_{eff}^4(T_i)}}
\intertext{where}
\delta k_{eff} &= \mbox{statistical error for $k_{eff}$ from SERPENT-2 
output.} 
\nonumber
\end{align}
Notably, other sources of uncertainty are neglected, such as cross-section 
measurement error and approximations inherent in the density dependence on 
temperature.

When the fuel salt temperature increases, the density of the salt decreases, 
but at the same time, the total volume of fuel salt in the 
core remains constant because it
is bounded by the vessel. When the graphite 
temperature increases, the density of
graphite decreases, creating additional 
space for the salt. The cross-section temperatures for the fuel and moderator 
were changed from 900 to 1000 K to determine the temperature coefficients. 
This work considered five different cases:
\begin{enumerate}
	\item Fuel salt temperature (Doppler Effect) rising from 900 to 1000 K 
	(first row  in Table~\ref{tab:tcoe}).
	\item Fuel salt density decreasing from 3.3 to 3.233 g/cm$^3$ 
	(density change caused by temperature increase from	900 to 1000 K).
	\item Total fuel salt temperature (Doppler+density) rising from 900 to 
	1000 K.	
	\item Graphite temperature (Doppler Effect) rising from 900 to 1000 K.
	\item Whole reactor temperature rising from 900 K to 1000 K.
\end{enumerate}

In the first case, the fuel temperature change only impacts cross-section 
temperature. In the second case, changes in the fuel temperature only impact 
density, and the third case takes into account both effects. The geometry for 
these three cases is unchanged because the fuel is a liquid. However, when 
the graphite blocks heat up, both the density and the geometry changing due 
to the thermal expansion of solid graphite. The graphite linear thermal 
expansion is not a dominating factor \cite{li_optimization_2018}, and herein 
we focus only on Doppler Effect for the moderator temperature coefficient.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} [b!]
	\caption{Temperature coefficients of reactivity for 3 different initial 
		fuel salt compositions at startup and equilibrium. Confidence interval 
		$\pm\sigma$ for all coefficients is between $0.11$ and $0.16$ pcm/K).}
	\begin{tabularx}{\textwidth}{ p{0.27\textwidth} | X X  X X  X X } \hline
		\multirow{3}{*}{\shortstack{Reactivity coefficient \\ (pcm/K)}} 
		& 
		\multicolumn{6}{c}{Startup fissile material} \\ \cline{2-7}
		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
		\multicolumn{2}{c}{TRU} \\ \cline{2-7}
		\space  & Initial & Equil. & Initial & Equil. & Initial & 
		Equil. \\ \hline
		Fuel salt temperature&$-4.96$&$-5.26$&$-4.99$&$-3.12$&$-3.23$&$-1.97$ 
		\\ 
		Fuel salt density&$+1.49$&$+2.34$&$+1.54$&$-1.58$&$-0.37$&$-1.62$ \\
		Total salt fuel&$-3.77$&$-2.83$&$-3.22$&$-4.23$&$-3.25$&$-3.69$ \\ 
		\hline
		Graphite temperature&$+1.45$&$+0.45$&$-2.68$&$-1.37$&$-1.44$&$-1.14$ 
		\\	\hline
		Total core&$-1.77$&$-2.59$&$-6.54$&$-5.06$&$-4.79$&$-4.76$ \\ \hline
	\end{tabularx}
	\label{tab:tcoe}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The \gls{FTC} is negative for all considered fuel compositions due to thermal 
Doppler broadening of the resonance capture cross-sections in the thorium. For the 
$^{233}$U case, the \gls{FTC} decreases in magnitude by $-25\%$ due to neutron 
spectrum hardening during the reactor operation. For Pu reactor-grade and TRU 
cases, the \gls{FTC} becomes more negative at the equilibrium, by $+31\%$ and 
$+14\%$, respectively. Spectrum softening for these fueling cases positively 
affects the \gls{FTC} magnitude, and this effect seems to be proportional to 
the spectrum shift.

The \gls{MTC} for the $^{233}$U case is positive and decreases during reactor 
operation because of spectrum hardening with fuel depletion. For other cases, 
the \gls{MTC} is negative and also decreasing in magnitude during the reactor 
operation. Finally, the total temperature coefficient of reactivity is 
strongly negative for all considered scenarios but decreases in magnitude 
during reactor operation due to spectral shift. Notably, the total temperature 
coefficient is the most negative for the Pu reactor-grade case at startup, 
which has the hardest neutron spectrum (Figure~\ref{fig:spectrumFLUX110vC}). 
These coefficients agree with earlier estimates for SD-TMSR 
\cite{li_optimization_2018, ashraf2019whole_core} and \gls{MSBR} 
\cite{rykhlevskii2019modeling,  
rykhlevskii_full-core_2017,robertson_conceptual_1971}.

Even after 30 years of operation, the total temperature coefficient of 
reactivity remains relatively large and negative (in the range between $-2.59$ 
and $-5.06$ pcm/K) comparing with the conventional \gls{PWR}, which has 
temperature coefficient of about $-1.71$ $pcm/^{\circ}F\approx -3.08$ $pcm/K$ 
\cite{forget_integral_2018}), and allows excellent reactor stability and 
control. The additional analysis must be performed taking graphite moderator 
density change and linear thermal expansion into account, but material 
properties for the SD-TMSR graphite are not available in published literature. 
Alternatively, relatively well-studied reactor graphite (e.g., AXQ graphite 
\cite{robertson_conceptual_1971}) can be considered as a candidate for the 
SD-TMSR concept.

\subsection{Six factor analysis}
The effective multiplication factor can be expressed as follows:
\begin{align}
k_{eff} &= k_{inf} P_f  P_t = \eta f p \epsilon P_f P_t
\intertext{where}
\eta     &= \mbox{thermal fission factor} \nonumber \\
f        &= \mbox{thermal utilization factor} \nonumber \\
p        &= \mbox{resonance escape probability} \nonumber \\
\epsilon &= \mbox{fast fission factor} \nonumber \\
P_f      &= \mbox{fast non-leakage probability} \nonumber \\
P_t      &= \mbox{thermal non-leakage probability.} \nonumber
\end{align}

Table~\ref{tab:six_factor} summarizes the six factors for 3 different initial 
fuel salt compositions at startup and equilibrium. By using SERPENT-2 built-in 
online reprocessing capabilities, all six factors have been calculated at the 
beginning of the operation and after 30 years of operation. Neutron population 
and number of active/inactive cycles were selected to obtain $k_{eff}$ 
statistical uncertainty less than 12 pcm. The fast and thermal non-leakage 
probabilities  remain constant regardless of initial fissile material and 
neutron spectrum shift during operation. The thermal utilization factor (f) 
remains almost constant during operation for $^{233}$U and TRU cases but 
considerably declines for Pu case due to significant neutron spectrum 
softening.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} [ht!]
	\caption{Six factors for the SD-TMSR model for 3 different initial 
		fuel salt compositions at startup and equilibrium.}
	\begin{tabularx}{\textwidth}{ X | X X  X X  X X } \hline
		\multirow{3}{*}{Factor}  & \multicolumn{6}{c}{Startup fissile 
			material} \\ \cline{2-7}
		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
		\multicolumn{2}{c}{TRU} \\ \cline{2-7}
		\space  & Initial & Equil & Initial & Equil & Initial & Equil \\ \hline
		$\eta$  & 1.26 & 1.40 & 1.66 & 1.44 & 1.59 & 1.31 \\ 
		f       & 0.97 & 0.98 & 0.96 & 0.76 & 0.80 & 0.75 \\
		p       & 0.54 & 0.43 & 0.26 & 0.16 & 0.17 & 0.15 \\
		$\epsilon$ & 1.49 & 1.67 & 2.45 & 5.87 & 4.83 & 6.81 \\
		P$_f$   & 0.99 & 0.99 & 0.99 & 0.99& 0.99 & 0.99 \\
		P$_t$   & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ \hline
	\end{tabularx}
	\label{tab:six_factor}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In contrast, the neutron reproduction factor ($\eta$), resonance escape 
probability ($p$), and fast fission factor ($\epsilon$) differ notably between 
initial and equilibrium state for all three initial fissile materials. The 
fast fission factor ($\epsilon$) is much larger at startup for Pu and TRU 
cases because these initial fissile materials provided a much harder neutron 
spectrum than $^{233}$U, and $\epsilon$ grows throughout the core's lifetime. 
Conversely, the resonance escape probability decreases during reactor 
operation. The thermal fission factor increases during reactor operation for 
the $^{233}$U as initial fuel due to the accumulation of fissile plutonium 
isotopes, which produce more neutrons per fission ($\nu$). The other two 
scenarios demonstrated opposite behavior: plutonium isotopes with large 
neutrons per fission production ($\nu$) are gradually substituted with the 
$^{233}$U, which has lower $\nu$ \cite{sjostrand_cross_1960}. This six 
factors' evolution agrees with previously determined evolution parameters for 
a similar single-fluid double-zone \gls{MSBR} \cite{ashraf2019whole_core, 
rykhlevskii2019modeling, park_whole_2015}.

>>>>

\subsection{Neutron flux}
Figures~\ref{fig:fast_flux} and \ref{fig:thermal_flux} show the radial 
distribution of fast (energy range between 0.625 eV and 20 MeV) and thermal 
(energy range between 10$^{-5}$ eV and 0.625 eV) neutron flux for three 
different initial fissile materials in the fuel salt ($^{233}$U, reactor-grade 
Pu, TRU) at startup and at equilibrium (after $\approx 30$ years of 
operation). Actinides' evolution and poisonous fission product accumulation 
for various initial fissile compositions demonstrates the different effects on 
the SD-TMSR neutronics performance. For the $^{233}$U case, the thermal 
neutron flux is suppressed at equilibrium because fissile $^{233}$U in the 
core is being substituted with heavier fissile actinides: $^{235}$U, 
$^{239}$Pu, and $^{241}$Pu. This agrees with results in literature 
\cite{rykhlevskii2019modeling, ashraf2019whole_core}.
\begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
	\includegraphics[width=\textwidth]{radial_fast_flux_init_vs_eq.png} 
	\caption{Radial fast neutron flux distribution for 3 different initial 
		fuel salt compositions at startup and equilibrium (the fast flux 
		confidence interval $\pm\sigma<2.5$\% for all cases).}
	\label{fig:fast_flux}
\end{figure}

Opposite behavior is observed for the reactor-grade Pu and TRU cases. For  
these cases, the thermal neutron flux increases during operation while fast 
neutron flux decreases. Fissile Pu nuclides (generate relatively hard 
spectrum) from initial fuel salt composition are gradually substituted with  
$^{233}$U (generates relatively soft spectrum), produced from fertile 
$^{232}$Th. During reactor operation, $^{233}$U becomes the primary fissile 
isotope, which softening the neutron spectrum of the reactor. 
\begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
	\includegraphics[width=\textwidth]{radial_thermal_flux_init_vs_eq.png} 
	\caption{Radial thermal neutron flux distribution for 3 different initial 
		fuel salt compositions at startup and equilibrium (the thermal flux 
		confidence interval $\pm\sigma<1.6$\% for all cases).}
	\label{fig:thermal_flux}
\end{figure}

More changes in thermal neutron flux shape and magnitude for the 
$^{233}$U case are observed in the inner core zone ($R\lesssim150$) than 
in the outer core zone. In contrast, for the reactor-grade Pu and TRU cases, 
significant changes are observed for thermal neutron flux in the outer core 
zone and reflector. Additionally, Figure~\ref{fig:thermal_flux} shows 
relatively large changes in thermal flux leakage from the core for the Pu and 
TRU cases. The SD-TMSR core design was optimized for $^{233}$U  
\cite{li_optimization_2018}; thus, the core geometry (e.g., channels lattice 
pitch) must be re-optimized for another type of fuel to obtain better 
neutronics performance.

\subsection{Temperature coefficient of reactivity}
The temperature coefficient of reactivity quantifies reactivity changes due to 
temperature increase in the core and is calculated in this work as follows:
\begin{align}
\alpha &= \frac{k_{eff}(T_{i+1}) - k_{eff}(T_i)}{k_{eff}(T_{i+1}) 
	k_{eff}(T_{i}) (T_{i+1} - T_i)}
\intertext{where}
k_{eff} &= \mbox{effective multiplication factor} \nonumber \\
T_i &= \mbox{fuel salt temperature in (900 K, 1000 K).} \nonumber
\end{align}

Table~\ref{tab:tcoe} summarizes temperature coefficients calculated for three 
different initial fissile loads at startup and at equilibrium. By propagating 
the $k_{eff}$ statistical error provided by SERPENT-2, uncertainty for each 
temperature coefficient is calculated using the following formula:
\begin{align}
\delta\alpha &= \abs{\frac{1}{T_{i+1} - T_i}} \sqrt{\frac{\delta 
		k_{eff}^2(T_{i+1})}{k_{eff}^4(T_{i+1})}  
	+ \frac{\delta k_{eff}^2(T_i)}{k_{eff}^4(T_i)}}
\intertext{where}
\delta k_{eff} &= \mbox{statistical error for $k_{eff}$ from SERPENT-2 
output.} 
\nonumber
\end{align}
Other sources of uncertainty are neglected, such as cross-section measurement 
error and approximations inherent in the density dependence on temperature.

When the fuel salt temperature increases, the density of the salt decreases; 
however, the total volume of fuel salt in the core remains constant because it
is bounded by the vessel. When the graphite temperature increases, the density 
of graphite decreases, creating additional space for the salt. The 
cross-section temperatures for the fuel and moderator were changed from 900 to 
1000 K to determine the temperature coefficients. This work considers five 
different cases:
\begin{enumerate}
	\item Fuel salt temperature (Doppler Effect) rising from 900 to 1000 K 	
	(first row in Table~\ref{tab:tcoe}).
	\item Fuel salt density decreasing from 3.3 to 3.233 g/cm$^3$ 
	(density change caused by temperature increase from	900 to 1000 K).
	\item Total fuel salt temperature (Doppler+density) rising from 900 to 
	1000 K.	
	\item Graphite temperature (Doppler Effect) rising from 900 to 1000 K.
	\item Whole reactor temperature rising from 900 K to 1000 K.
\end{enumerate}

In the first case, the fuel temperature change only impacts cross-section 
temperature. In the second case, changes in the fuel temperature only impact 
density, and the third case takes into account both effects. The geometry for 
these three cases is unchanged because the fuel is a liquid. However, when 
the graphite blocks heat up, both the density and the geometry change due 
to the thermal expansion of solid graphite. The graphite linear thermal 
expansion is not a dominating factor \cite{li_optimization_2018}, and herein 
we focus only on the Doppler Effect for the moderator temperature coefficient.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} [b!]
	\caption{Temperature coefficients of reactivity for 3 different initial 
		fuel salt compositions at startup and equilibrium. Confidence interval 
		$\pm\sigma$ for all coefficients is between $0.11$ and $0.16$ pcm/K).}
	\begin{tabularx}{\textwidth}{ p{0.27\textwidth} | X X  X X  X X } \hline
		\multirow{3}{*}{\shortstack{Reactivity coefficient \\ (pcm/K)}} 
		& 
		\multicolumn{6}{c}{Startup fissile material} \\ \cline{2-7}
		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
		\multicolumn{2}{c}{TRU} \\ \cline{2-7}
		\space  & Initial & Equil. & Initial & Equil. & Initial & 
		Equil. \\ \hline
		Fuel salt temperature&$-4.96$&$-5.26$&$-4.99$&$-3.12$&$-3.23$&$-1.97$ 
		\\ 
		Fuel salt density&$+1.49$&$+2.34$&$+1.54$&$-1.58$&$-0.37$&$-1.62$ \\
		Total salt fuel&$-3.77$&$-2.83$&$-3.22$&$-4.23$&$-3.25$&$-3.69$ \\ 
		\hline
		Graphite temperature&$+1.45$&$+0.45$&$-2.68$&$-1.37$&$-1.44$&$-1.14$ 
		\\	\hline
		Total core&$-1.77$&$-2.59$&$-6.54$&$-5.06$&$-4.79$&$-4.76$ \\ \hline
	\end{tabularx}
	\label{tab:tcoe}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The \gls{FTC} is negative for all considered fuel compositions due to thermal 
Doppler broadening of the resonance capture cross sections in the thorium. For 
the $^{233}$U case, the \gls{FTC} decreases in magnitude by $25\%$ due to 
neutron spectrum hardening during the reactor operation. For reactor-grade Pu 
and TRU cases, the \gls{FTC} increases in magnitude at equilibrium, by $31\%$ 
and $14\%$, respectively. Spectrum softening for these fueling cases 
positively affects the \gls{FTC} magnitude, and this effect seems to be 
proportional to the spectrum shift.

The \gls{MTC} for the $^{233}$U case is positive and decreases during reactor 
operation because of spectrum hardening with fuel depletion. For other cases, 
the \gls{MTC} is negative and also decreases in magnitude during reactor  
operation. Finally, the total temperature coefficient of reactivity is 
strongly negative for all considered scenarios but decreases in magnitude 
during reactor operation due to spectral shift. Notably, the total temperature 
coefficient is the most negative for the reactor-grade Pu case at startup, 
which has the hardest neutron spectrum (Figure~\ref{fig:spectrumFLUX110vC}). 
These coefficients agree with earlier estimates for the SD-TMSR 
\cite{li_optimization_2018, ashraf2019whole_core} and \gls{MSBR} 
\cite{rykhlevskii2019modeling, rykhlevskii_full-core_2017,  
robertson_conceptual_1971}.

Even after 30 years of operation, the total temperature coefficient of 
reactivity remains relatively large and negative (in the range between $-2.59$ 
and $-5.06$ pcm/K) compared to the conventional \gls{PWR}, which has 
temperature coefficient of about $-1.71$ $pcm/^{\circ}F\approx -3.08$ $pcm/K$ 
\cite{forget_integral_2018}, and allows excellent reactor stability and 
control. The additional analysis must be performed taking graphite moderator 
density change and linear thermal expansion into account, but material 
properties for the SD-TMSR graphite are not available in published literature. 
Relatively well-studied reactor graphite (e.g., AXQ graphite 
\cite{robertson_conceptual_1971}) can be considered as a candidate for the 
SD-TMSR concept.

\subsection{Six factor analysis}
The effective multiplication factor can be expressed as follows:
\begin{align}
k_{eff} &= \eta f p \epsilon P_f P_t
\intertext{where}
\eta     &= \mbox{thermal fission factor} \nonumber \\
f        &= \mbox{thermal utilization factor} \nonumber \\
p        &= \mbox{resonance escape probability} \nonumber \\
\epsilon &= \mbox{fast fission factor} \nonumber \\
P_f      &= \mbox{fast non-leakage probability} \nonumber \\
P_t      &= \mbox{thermal non-leakage probability.} \nonumber
\end{align}

Table~\ref{tab:six_factor} summarizes the six factors for 3 different initial 
fuel salt compositions at startup and equilibrium. By using SERPENT-2 built-in 
online reprocessing capabilities, all six factors are calculated at the 
beginning of the operation and after 30 years of operation. Neutron population 
and number of active/inactive cycles were selected to obtain $k_{eff}$ 
statistical uncertainty less than 12 pcm. The fast and thermal non-leakage 
probabilities remain constant regardless of initial fissile material and 
neutron spectrum shift during operation. The thermal utilization factor (f) 
remains almost constant during operation for the $^{233}$U and TRU cases but 
considerably declines for the Pu case due to significant neutron spectrum 
softening.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} [ht!]
	\caption{Six factors for the SD-TMSR model for 3 different initial 
		fuel salt compositions at startup and equilibrium.}
	\begin{tabularx}{\textwidth}{ X | X X  X X  X X } \hline
		\multirow{3}{*}{Factor}  & \multicolumn{6}{c}{Startup fissile 
			material} \\ \cline{2-7}
		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
		\multicolumn{2}{c}{TRU} \\ \cline{2-7}
		\space  & Initial & Equil & Initial & Equil & Initial & Equil \\ \hline
		$\eta$  & 1.26 & 1.40 & 1.66 & 1.44 & 1.59 & 1.31 \\ 
		f       & 0.97 & 0.98 & 0.96 & 0.76 & 0.80 & 0.75 \\
		p       & 0.54 & 0.43 & 0.26 & 0.16 & 0.17 & 0.15 \\
		$\epsilon$ & 1.49 & 1.67 & 2.45 & 5.87 & 4.83 & 6.81 \\
		P$_f$   & 0.99 & 0.99 & 0.99 & 0.99& 0.99 & 0.99 \\
		P$_t$   & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ \hline
	\end{tabularx}
	\label{tab:six_factor}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In contrast, the neutron reproduction factor ($\eta$), resonance escape 
probability ($p$), and fast fission factor ($\epsilon$) differ notably between 
the initial and equilibrium state for all three initial fissile materials.  
$\epsilon$ is much larger at startup for the Pu and TRU cases because these 
initial fissile materials provide a much harder neutron spectrum than 
$^{233}$U, and $\epsilon$ grows throughout the core's lifetime. Conversely, 
$p$ decreases during reactor operation. The thermal fission factor ($\eta$)  
increases during reactor operation for the $^{233}$U as initial fuel due to 
the accumulation of fissile plutonium isotopes, which produce more neutrons 
per fission ($\nu$). The other two scenarios demonstrate opposite behavior: 
plutonium isotopes with large $\nu$ are gradually substituted with $^{233}$U, 
which has a lower $\nu$ \cite{sjostrand_cross_1960}. This six factors' 
evolution agrees with previously determined evolution parameters for a similar 
single-fluid double-zone \gls{MSBR} \cite{ashraf2019whole_core, 
rykhlevskii2019modeling, park_whole_2015}.
